---
title: "World Happiness 2021"
author: "Silvana Avramska Lukarska"
date: "5/5/2021"
output: html_document
---
In the following, we are going to look at the levels of happiness around the world. We will use the World Happiness Report which is a landmark survey of the state of global happiness. The happiness scores and rankings use data from the Gallup World Poll . The columns following the happiness score estimate the extent to which each of six factors – economic production, social support, life expectancy, freedom, absence of corruption, and generosity – contribute to making life evaluations higher in each country than they are in Dystopia, a hypothetical country that has values equal to the world’s lowest national averages for each of the six factors. They have no impact on the total score reported for each country, but they do explain why some countries rank higher than others. The data can be found at [Kaggle][Kaggle]

[Kaggle]: "https://www.kaggle.com/ajaypalsinghlo/world-happiness-report-2021"


```{r echo=FALSE, message=FALSE, warning = FALSE}
library(plotly)

data <- read.csv("world-happiness-report-2021.csv")
#dim(data)
#str(data)

#data$Regional.indicator <- as.factor(data$Regional.indicator)
```


```{r echo=FALSE, message=FALSE, warning = FALSE}
fig <- plot_ly(data, x=~Healthy.life.expectancy, y=~Ladder.score, mode="markers",
               color=~Regional.indicator, size=~Logged.GDP.per.capita,
               text=~paste("Country:", Country.name, "<br>Ladder score:", Ladder.score, 
                           "<br>GDP per capita:", Logged.GDP.per.capita ),
               width = 1000, height = 600)

fig %>% layout(xaxis=list(title="Healthy Life Expectancy"),
               yaxis=list(title="Ladder Score"))
```
